Openness and computational reproducibility in plant pathology: where we stand and a way forward

### 2024-08-08 analysis/paper/paper.Rmd
Fix missing "." and linebreaks

The analyses were undecided when predicting both the effects of the five-year impact factor on the availability of computational methods (code) and data
The effect of five-year impact factor (Median = 0.45, 95% CI [-0.05, 1.04]) had a
96.00% probability of being positive (> 0), 94.25% of being significant
(> 0.05), and 72.26% of being large (> 0.30).
The estimation successfully converged (Rhat = 1.000) and the indices are reliable (ESS = 14595).
The effect of the five-year impact factor on data availability (Median = 0.15, 95% CI [-3.75e-03, 0.30]) had a 97.21% probability of being positive (> 0), 89.41% of being
significant (> 0.05), and 2.48% of being large (> 0.30).
The estimation successfully converged (Rhat = 1.000) and the indices are reliable (ESS = 4188).

>>>>

The analyses were undecided when predicting both the effects of the five-year impact factor on the availability of computational methods (code) and data.
The effect of five-year impact factor (Median = 0.45, 95% CI [-0.05, 1.04]) had a 96.00% probability of being positive (> 0), 94.25% of being significant (> 0.05), and 72.26% of being large (> 0.30).
The estimation successfully converged (Rhat = 1.000) and the indices are reliable (ESS = 14595).
The effect of the five-year impact factor on data availability (Median = 0.15, 95% CI [-3.75e-03, 0.30]) had a 97.21% probability of being positive (> 0), 89.41% of being significant (> 0.05), and 2.48% of being large (> 0.30).
The estimation successfully converged (Rhat = 1.000) and the indices are reliable (ESS = 4188).
